fromFobLisa, Version 2

### 2018-03-02 CreData/fromFobLisa.Rmd
continue

```{r kommuner}
ourkom <- c(2406, 2414, 2417, 2418, 2480, 2482)
ourkom <- c(ourkom, 2411, 2412, 2413, 2416, 2415, 2461, 2407, 2402, 2408)
```

@@

```{r mat60}
library(eha)
indx <- match(fob60$LINNEID, per$LINNEID)
fob60$birthdate <- per$birthdate[indx]
lim <- as.numeric(toTime("1940-11-01"))
fob60 <- fob60[fob60$birthdate < lim, ]
indx <- match(fob60$LINNEID, per$LINNEID) # NOTE: Necessary!
fob60$enter <- lim + 20 - fob60$birthdate
dd <- per$deathdate[indx]
fob60$event <- !(is.na(dd)) & (dd <= lim + 25) # NOTE: 40 --> 25!
fob60$exit <- fob60$enter + 5
fob60$exit[fob60$event] <- dd[fob60$event] - fob60$birthdate[fob60$event]
head(fob60)
```

>>>>

```{r kommuner}
ourkom <- c(2406, 2414, 2417, 2418, 2480, 2482)
ourkom <- c(ourkom, 2411, 2412, 2413, 2416, 2415, 2461, 2407, 2402, 2408)
fob <- fob[fob$KOMMUN %in% ourkom, ]
```

@@

```{r mat60}
library(eha)
indx <- match(fob60$LINNEID, per$LINNEID)
fob60$birthdate <- per$birthdate[indx]
fob60$fobdate <- as.numeric(toTime("1960-11-01"))
##lim <- as.numeric(toTime("1940-11-01"))
##fob60 <- fob60[fob60$birthdate < lim, ]
indx <- match(fob60$LINNEID, per$LINNEID) # NOTE: Necessary!
fob60$enter <- fob60$fobdate - fob60$birthdate
dd <- per$deathdate[indx]
##fob60$event <- !(is.na(dd)) & (dd <= lim + 25) # NOTE: 40 --> 25!
fob60$event <- !(is.na(dd)) & (dd <= fob60$fobdate +5)
fob60$exit <- fob60$enter + 5
fob60$exit[fob60$event] <- dd[fob60$event] - fob60$birthdate[fob60$event]
head(fob60)
```
